The Space of Feasible Execution Times for Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-09-26 dit-paper_ieee.tex
added "Paris"
merge

\author{
\IEEEauthorblockN{Thomas Chapeaux and Paul Rodriguez}
\IEEEauthorblockA{Universit\'{e} Libre de Bruxelles / ECE\\
tchapeau@ulb.ac.be, paurodri@ulb.ac.be}
\and
\IEEEauthorblockN{Laurent George}
\IEEEauthorblockA{University of Paris-Est / ECE Paris\\
lgeorge@ieee.org}
\and
\IEEEauthorblockN{Jo\"el Goossens}
\IEEEauthorblockA{Universit\'{e} Libre de Bruxelles\\
joel.goossens@ulb.ac.be}
}

@@

\begin{abstract}
	Sensitivity analysis for real-time systems provides efficient methods to determine feasibility
	conditions in the case of changes in task parameters, such as
	different WCET values when porting a system to a different platform. The \mbox{C-space} defines the space of execution
	times for which a system is feasible, which can help system designers to more easily check 
	if a task set is feasible on a set of candidate platforms. This paper extends previous works
	generalizing the description of the C-space for Earliest Deadline First
	scheduling to systems with initial task offsets. The feasibility gain offered
	by offsets is then expressed as the volume ratio between the C-space of an
	asynchronous system and its corresponding synchronous system when offsets are randomly chosen. The problem
	requires solving multiple similar instances of the Chinese Remainder Problem,
	for which an efficient algorithm in this context is provided. We show that even for random offsets, the gain can reach 15%.
\end{abstract}

@@

		This system is equivalent to multiple instances (one per combination of $a_i$
		values) of the Chinese Remainder Problem (CRP) where the goal is to find the
		value of $t_d$ such that it is congruent to $a_i+O_i$ modulo $T_i$ for all
		tasks $\tau_i$ in $\tau$. To find the FPDIT it is to the best of our knowledge
		necessary to solve the problem on all combinations of $a_i$ values and then
		to compute the minimum solution. We define $x_i = a_i+O_i$ and $n_i = T_i$ for
		clarity in the context of the CRP. One instance of this problem is guaranteed
		to have at least one solution modulo $H$ for given values of $a_i$ if
		Condition~\ref{eq:CRPcond} is satisfied \cite{knuth1969art}:
		\begin{equation}
			\label{eq:CRPcond}
			x_i \equiv x_j \; (\operatorname{mod} \; \operatorname{gcd}(n_i, n_j))
			\; \forall \tau_i,\tau_j \in \tau
		\end{equation}
		Condition~\ref{eq:CRPcond} means that DITs might still exist even though in
		the general case task periods will not necessarily be pairwise coprime.
% 		We now present an example of such a system.\\
%
% 		\begin{center}
% 			\begin{tabular}{|r|c|c|c|c|}
% 				\hline
% 							& $O_i$ & $C_i$ & $D_i$ & $T_i$ \\ \hline
% 				$\tau_1$ 	& 0 	& $C_1$ & 3 	& 4\\ \hline
% 				$\tau_2$ 	& 2 	& $C_2$ & 7 	& 8\\ \hline
% 			\end{tabular}
% 		\end{center}
%
% 		Here, the possible values of $a_1$ are 3 and 4, and the possible values
% 		of $a_2$ are 7 and 8. For a FPDIT to exist, one of the following
% 		conditions must be fulfilled:
% 		\[
% 			\left[
% 			\begin{array}{c}
% 				3 + 0 \equiv 7 + 2 \; (\operatorname{mod} \; 4 ) \\
% 				3 + 0 \equiv 8 + 2 \; (\operatorname{mod} \; 4 ) \\
% 				4 + 0 \equiv 7 + 2 \; (\operatorname{mod} \; 4 ) \\
% 				4 + 0 \equiv 8 + 2 \; (\operatorname{mod} \; 4 ) \\
% 			\end{array}
% 			\right.
% 		\]
% 		However neither is, which means the system has
% 		no FPDIT (and no other DIT than $t=0$).

>>>>

\author{
\IEEEauthorblockN{Thomas Chapeaux and Paul Rodriguez}
\IEEEauthorblockA{Universit\'{e} Libre de Bruxelles / ECE Paris\\
tchapeau@ulb.ac.be, paurodri@ulb.ac.be}
\and
\IEEEauthorblockN{Laurent George}
\IEEEauthorblockA{University of Paris-Est / ECE Paris\\
lgeorge@ieee.org}
\and
\IEEEauthorblockN{Jo\"el Goossens}
\IEEEauthorblockA{Universit\'{e} Libre de Bruxelles\\
joel.goossens@ulb.ac.be}
}

@@

\begin{abstract}
	Sensitivity analysis for real-time systems provides efficient methods to determine feasibility
	conditions in the case of changes in task parameters, such as
	different WCET values when porting a system to a different platform. The \mbox{C-space} defines the space of execution
	times for which a system is feasible, which can help system designers to more easily check
	if a task set is feasible on a set of candidate platforms. This paper extends previous works
	generalizing the description of the C-space for Earliest Deadline First
	scheduling to systems with initial task offsets. The feasibility gain offered
	by offsets is then expressed as the volume ratio between the C-space of an
	asynchronous system and its corresponding synchronous system when offsets are randomly chosen. The problem
	requires solving multiple similar instances of the Chinese Remainder Problem,
	for which an efficient algorithm in this context is provided. We show that even for random offsets, the gain can reach 15\%.
\end{abstract}

@@

		This system is equivalent to multiple instances (one per combination of $a_i$
		values) of the Chinese Remainder Problem (CRP) where the goal is to find the
		value of $t_d$ such that it is congruent to $a_i+O_i$ modulo $T_i$ for all
		tasks $\tau_i$ in $\tau$. To find the FPDIT it is to the best of our knowledge
		necessary to solve the problem on all combinations of $a_i$ values and then
		to compute the minimum solution. We define $x_i = a_i+O_i$ and $n_i = T_i$ for
		clarity in the context of the CRP. One instance of this problem is guaranteed
		to have at least one solution modulo $H$ for given values of $a_i$ if and only if
		Condition~\ref{eq:CRPcond} is satisfied \cite{knuth1969art}:
		\begin{equation}
			\label{eq:CRPcond}
			x_i \equiv x_j \; (\operatorname{mod} \; \operatorname{gcd}(n_i, n_j))
			\; \forall \tau_i,\tau_j \in \tau
		\end{equation}
		Condition~\ref{eq:CRPcond} means that DITs might still exist even though in
		the general case task periods will not necessarily be pairwise coprime.
% 		We now present an example of such a system.\\
%
% 		\begin{center}
% 			\begin{tabular}{|r|c|c|c|c|}
% 				\hline
% 							& $O_i$ & $C_i$ & $D_i$ & $T_i$ \\ \hline
% 				$\tau_1$ 	& 0 	& $C_1$ & 3 	& 4\\ \hline
% 				$\tau_2$ 	& 2 	& $C_2$ & 7 	& 8\\ \hline
% 			\end{tabular}
% 		\end{center}
%
% 		Here, the possible values of $a_1$ are 3 and 4, and the possible values
% 		of $a_2$ are 7 and 8. For a FPDIT to exist, one of the following
% 		conditions must be fulfilled:
% 		\[
% 			\left[
% 			\begin{array}{c}
% 				3 + 0 \equiv 7 + 2 \; (\operatorname{mod} \; 4 ) \\
% 				3 + 0 \equiv 8 + 2 \; (\operatorname{mod} \; 4 ) \\
% 				4 + 0 \equiv 7 + 2 \; (\operatorname{mod} \; 4 ) \\
% 				4 + 0 \equiv 8 + 2 \; (\operatorname{mod} \; 4 ) \\
% 			\end{array}
% 			\right.
% 		\]
% 		However neither is, which means the system has
% 		no FPDIT (and no other DIT than $t=0$).
